A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
started to work on results chapter -- some discussion of data representativity. Might be better in the discussion

- Characteristics and map of final dataset

- Absolute and relative temporal development of traits by region

>>>>

Figure \ref{development_burial_type} and \ref{development_burial_construction} show the region wise timeseries of trait occurrence. The figure part A with absolute numbers indicates areas and timeperiods with a lot, and others with very few points of data. For some there is not enough information to make any decision about the relative dominance and for many the general relevance and accuracy of the resulting timeseries can be questioned. There's a variety of reasons for this:

1. The data in Radon-B depends on the projects and interests of the involved researchers: The data was collected as needed rather then systematically for all of europe.

2. The availability of ^14^C dates for a region and period in the literature depends on whether a modern research project took place within this context. Besides the research interets of researchers and institutions, there are also political reasons why an area might be better or worse explored.

3. In the field of investigation of this work different research traditions meet, which in the past considered ^14^C data more or less essential for the construction of an absolute chronological assessment. In various Metal Age contexts, 14C data are inferior to the accuracy of relative chronological classifications - e.g. on the basis of primer typology - and are therefore used only sporadically to create absolute chronological fix points. Dendrochronological dating is preferred in moist soil contexts and when the necessary woods are available. The available ^14^C calibration curves form plateaus in some periods, which significantly limit the achievable dating accuracy of the data. If such an effect is known, then no data is ordered at all.

4. ^14^C dating requires a small but sufficiently contextualizable amount of organic finds. Due to the old wood and old water effect, short-lived sample materials such as bones of terrestrial organisms or charred cereal grains are preferred. The majority of ^14^C data for this work comes from bones and teeth. However, their preservation is subject to great differences depending on the soil [@brockPrescreeningTechniquesIdentification2010; @gordonSoilPHBone1981; @nielsen-marshBoneDiagenesisEuropean2007]. In many mineral soil contexts no sufficiently good, dateable material is available. This can affect entire regions, if, for example, poor bone preservation prevails in general as a result of low-calcification soils.
